Incentivizing Exploration with Unbiased Histories

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Expanded a bit more.

\section*{Summary: Incentivizing Exploration with Unbiased Histories
\\{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}}

In a social learning setting, there is a set of actions, each of which has a fixed but unknown expected payoff. Agents arrive one by one, each chooses an action with the goal of maximizing the payoff.  A disclosure policy coordinates the choices of the agents by sending messages about the history of past actions. These messages can alter agents' incentives towards \emph{exploration}, taking potentially sub-optimal actions for the sake of learning more about their rewards. The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; more specifically, so as to minimize the regret of the action sequence chosen by the agents. Prior work achieves much progress with disclosure policies that merely recommend an action to each user. (Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.

>>>>

\section*{Submission: Incentivizing Exploration with Unbiased Histories \\
{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}\\
{\large Workshop: Learning in the Presence of Strategic Behavior}
}

In a social learning setting, there is a set of actions, each of which has a fixed but unknown expected payoff. Agents arrive one by one, each chooses an action with the goal of maximizing the payoff.  A disclosure policy coordinates the choices of the agents by sending messages about the history of past actions. These messages can alter agents' incentives towards \emph{exploration}, taking potentially sub-optimal actions for the sake of learning more about their rewards. The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; specifically, so as to minimize the regret of the chosen action sequence.

Prior work achieves much progress with disclosure policies that merely recommend an action to each user, without any other supporting information, and sometimes recommend exploratory actions. (Absent agents' incentives, such policy is a multi-armed bandit algorithm.) All this work relies heavily on trust and rationality assumptions, standard in economic theory. However, these assumptions are quite problematic in the context of the motivating applications such as recommendation systems. It is very unclear whether users would know and understand some complicated disclosure policy announced  by the principal, let alone trust the principal to faithfully implement this policy. Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the possibility of being singled out for exploration.
